Disparate views of disparity

### 2017-11-01 Analysis/disparity_methods.Rmd
Updated pipeline

I then categorised the data as follwos.
<!-- @@@ -->

@@

>>>>

I then categorised the data as follows.
<!-- @@@ -->

@@

<!-- 
How many studies use such and such definition: disparate views on disparity -> but maybe disparity is a vague concept?
How many studies use different definition for such or such parameter recorded: on average, disparity is defined as a single thing...

Parallel with diversity: it was a blurry thing - check out different diversity literature.
 -->

# Supplementary

## Number of papers collected for each parameter

```{r, fig.width = 12, fig.height = 12}
## Get the data for cumulative curves
total_cumulative <- data_raw[,c(1,3)]
#data_type_cumulative <- data_raw[,c(1,4)]

## Transform the cumulative data into binary
results <- grep("-", total_cumulative[,2])
results <- cbind(results, seq(1:length(results)))

plot(add, type = "line", xlab = "Number of Google Scholar matches", ylab = "Number of new entries")
